Add Data

### 2025-03-05 code.qmd
Specify knitr as engine for pages
We rely on knitr-specific syntax
throughout the tutorial, even in
instances where no code is executed.
Don't pass unncessary command line args
I think it's bad practice to skip them.
Minor improvements

---
title: "Add Code"
---

@@

With the data added to the project folder, you can now analyze them and describe the results.
For the purpose of this tutorial, we suggest to conduct a simple analysis
that explores whether the bill lengths of penguins vary between sex.
You can write your own or use the following example:

@@

```{.bash filename="Terminal"}
quarto add --no-prompt wjschne/apaquarto
```

>>>>

---
title: "Add Code"
engine: knitr
---

@@

With the data added to the project folder, you can now analyze them and describe the results.
For the purpose of this tutorial, we suggest to conduct a simple analysis
that explores whether the bill lengths of penguins vary depending on their sex.
You can write your own or use the following example:

@@

```{.bash filename="Terminal"}
quarto add wjschne/apaquarto
```

### 2025-03-05 data.qmd
Minor improvements

Privacy laws and contractual obligations may require you
to create a completely anonymized or synthetic data set[^anon-synth-tools] (if possible),
or prohibit any sharing of data, in which case you should provide a reference
to a data repository where they can be obtained from.
For further information, you can watch the talk "[Data anonymity](https://osf.io/j6fy8)"
by Felix Schönbrodt recorded during the LMU Open Science Center Summer School 2023
and have a look at [the accompanying slides](https://osf.io/z6gcu).
Another resource to look at is the presentation
"Creating reproducible packages when data are confidential" by @Vilhuber2024.
:::

>>>>

Privacy laws and contractual obligations may require you
to create an anonymized or synthetic data set[^anon-synth-tools],
in which case you should provide a reference
to a repository where the originally measured data can be obtained from.
For further information, you can watch the talk "[Data anonymity](https://osf.io/j6fy8)"
by Felix Schönbrodt recorded during the LMU Open Science Center Summer School 2023
and have a look at [the accompanying slides](https://osf.io/z6gcu).
Another resource to look at is the presentation
"Creating reproducible packages when data are confidential" by @Vilhuber2024.
:::
